---
title: "Regional News Platform — Digital KPI Report"
subtitle: "January Monthly Performance Analysis"
output:
  html_notebook: default
  pdf_document: default
---

> **Note:** This report was produced as part of a real-world workflow tracking digital audience performance for a regional broadcast news platform. Data values have been anonymized and simulated to protect proprietary company information. The code, analytical approach, and visualization logic reflect the actual methods used.

---

## Overview

This report tracks three core KPIs for a regional news platform's digital presence:

- **Online Visits** — total site traffic measured year-over-year
- **Video Plays** — on-demand and embedded video engagement
- **Streaming Minutes Watched** — live and on-demand streaming consumption

Each metric is examined through two lenses: a year-over-year bar chart comparing January performance across multiple years, and a monthly trend line tracking the full prior year into the current reporting period.

---

## Setup

```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
```

---

## Section 1: Online Visits

### Year-over-Year Comparison

The bar chart below compares January visits across years. The most recent year (2025) is highlighted in dark green to draw attention to current performance; the comparison low point (2023) is highlighted in red for context.

```{r}
# Simulated year-over-year visits data (values anonymized)
jan_visits <- data.frame(
  Year = c(2021, 2022, 2023, 2024, 2025),
  Visits = c(2100000, 2450000, 1980000, 2750000, 3100000)
)

jan_visits_graph <- ggplot(jan_visits, aes(
    x = Year,
    y = Visits,
    fill = ifelse(Year == 2023, "tomato3",
           ifelse(Year == 2025, "darkgreen", "grey"))
  )) +
  geom_bar(stat = "identity", width = .5) +
  geom_text(aes(label = comma(Visits)), vjust = -0.5, color = "black", size = 3) +
  labs(
    title = "January Performance — Regional News Platform",
    subtitle = "Online Visits: Year-over-Year",
    caption = "Source: Digital Analytics Platform"
  ) +
  scale_y_continuous(limits = c(0, 3800000), labels = comma) +
  scale_x_continuous(breaks = jan_visits$Year) +
  scale_fill_identity() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.6))

jan_visits_graph
```

**Takeaway:** January 2025 visits represent the platform's strongest January on record, recovering significantly from a 2023 dip and continuing an upward trend from 2024.

---

## Section 2: Video Plays

### Year-over-Year Comparison

Video plays reflect audience engagement with on-demand and embedded video content. The same color coding is applied — green for 2025, red for the comparison low year.

```{r}
# Simulated year-over-year video plays data (values anonymized)
jan_vp <- data.frame(
  Year = c(2021, 2022, 2023, 2024, 2025),
  `Video Plays` = c(3800000, 4200000, 3500000, 5100000, 6200000),
  check.names = FALSE
)

jan_vp_graph <- ggplot(jan_vp, aes(
    x = Year,
    y = `Video Plays`,
    fill = ifelse(Year == 2023, "tomato3",
           ifelse(Year == 2025, "darkgreen", "grey"))
  )) +
  geom_bar(stat = "identity", width = .5) +
  geom_text(aes(label = comma(`Video Plays`)), vjust = -0.5, color = "black", size = 3) +
  labs(
    title = "January Performance — Regional News Platform",
    subtitle = "Video Plays: Year-over-Year",
    caption = "Source: Digital Analytics Platform"
  ) +
  scale_y_continuous(limits = c(0, 7500000), labels = comma) +
  scale_x_continuous(breaks = jan_vp$Year) +
  scale_fill_identity() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.6))

jan_vp_graph
```

**Takeaway:** Video plays show strong year-over-year growth with a notable acceleration between 2024 and 2025, suggesting content strategy and platform changes are driving deeper video engagement.

---

## Section 3: Streaming Minutes Watched

### Year-over-Year Comparison

Streaming minutes watched is the most direct measure of live and on-demand streaming consumption — a key metric for broadcast platforms expanding their digital footprint.

```{r}
# Simulated year-over-year streaming minutes data (values anonymized)
jan_smw <- data.frame(
  Year = c(2021, 2022, 2023, 2024, 2025),
  `Streaming Minutes Watched` = c(2800000, 3600000, 3200000, 4400000, 5300000),
  check.names = FALSE
)

jan_smw_graph <- ggplot(jan_smw, aes(
    x = Year,
    y = `Streaming Minutes Watched`,
    fill = ifelse(Year == 2022, "blue",
           ifelse(Year == 2025, "darkgreen", "grey"))
  )) +
  geom_bar(stat = "identity", width = .5) +
  geom_text(aes(label = comma(`Streaming Minutes Watched`)), vjust = -0.5, color = "black", size = 3) +
  labs(
    title = "January Performance — Regional News Platform",
    subtitle = "Streaming Minutes Watched: Year-over-Year",
    caption = "Source: Digital Analytics Platform"
  ) +
  scale_y_continuous(limits = c(0, 6500000), labels = comma) +
  scale_x_continuous(breaks = jan_smw$Year) +
  scale_fill_identity() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.6))

jan_smw_graph
```

**Takeaway:** Streaming minutes watched has grown steadily since 2022, with 2025 reaching its highest January figure. This reflects both platform growth and audience behavior shifts toward streaming consumption.

---

## Section 4: Monthly Trend Analysis

The following line charts examine how each KPI trended across the most recent full annual cycle (February 2024 through January 2025). A linear trend line (`geom_smooth`) is overlaid to surface the directional signal beneath month-to-month variation.

### 4a: Visits — Monthly Trend

```{r message=FALSE, warning=FALSE}
# Simulated monthly visits data across the annual cycle (values anonymized)
Visits_yl <- data.frame(
  Month = c("February", "March", "April", "May", "June",
            "July", "August", "September", "October", "November", "December", "January"),
  Visits = c(2200000, 2400000, 2150000, 2300000, 2100000,
             2050000, 2200000, 2500000, 2650000, 2800000, 2900000, 3100000)
)

Visits_yl$Month <- factor(Visits_yl$Month,
  levels = c("February", "March", "April", "May", "June",
             "July", "August", "September", "October", "November", "December", "January"))

Visits_yl <- Visits_yl %>%
  group_by(Month) %>%
  summarise(Visits = sum(Visits, na.rm = TRUE)) %>%
  arrange(Month)

ggplot(data = Visits_yl, aes(x = Month, y = Visits, group = 1)) +
  geom_line(color = "steelblue", linewidth = 1) +
  geom_point(color = "steelblue", size = 2) +
  geom_smooth(method = "lm", se = FALSE, color = "darkgreen", linetype = "dashed") +
  scale_y_continuous(labels = comma) +
  labs(
    title = "Online Visits — Monthly Trend (Feb 2024 – Jan 2025)",
    caption = "Source: Digital Analytics Platform | Dashed line = linear trend"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### 4b: Video Plays — Monthly Trend

```{r message=FALSE, warning=FALSE}
# Simulated monthly video plays data (values anonymized)
video_plays_yl <- data.frame(
  Month = c("February", "March", "April", "May", "June",
            "July", "August", "September", "October", "November", "December", "January"),
  `Video Plays` = c(3900000, 4100000, 3800000, 4000000, 3700000,
                    3600000, 3900000, 4400000, 4700000, 5100000, 5500000, 6200000),
  check.names = FALSE
)

video_plays_yl$Month <- factor(video_plays_yl$Month,
  levels = c("February", "March", "April", "May", "June",
             "July", "August", "September", "October", "November", "December", "January"))

video_plays_yl <- video_plays_yl %>%
  group_by(Month) %>%
  summarise(`Video Plays` = sum(`Video Plays`, na.rm = TRUE)) %>%
  arrange(Month)

ggplot(data = video_plays_yl, aes(x = Month, y = `Video Plays`, group = 1)) +
  geom_line(color = "steelblue", linewidth = 1) +
  geom_point(color = "steelblue", size = 2) +
  geom_smooth(method = "lm", se = FALSE, color = "darkgreen", linetype = "dashed") +
  scale_y_continuous(labels = comma) +
  labs(
    title = "Video Plays — Monthly Trend (Feb 2024 – Jan 2025)",
    caption = "Source: Digital Analytics Platform | Dashed line = linear trend"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### 4c: Streaming Minutes Watched — Monthly Trend

```{r message=FALSE, warning=FALSE}
# Simulated monthly streaming minutes data (values anonymized)
smw_yl <- data.frame(
  Month = c("February", "March", "April", "May", "June",
            "July", "August", "September", "October", "November", "December", "January"),
  `Streaming Minutes Watched` = c(3100000, 3300000, 3000000, 3200000, 2900000,
                                   2800000, 3100000, 3600000, 3900000, 4200000, 4700000, 5300000),
  check.names = FALSE
)

smw_yl$Month <- factor(smw_yl$Month,
  levels = c("February", "March", "April", "May", "June",
             "July", "August", "September", "October", "November", "December", "January"))

smw_yl <- smw_yl %>%
  group_by(Month) %>%
  summarise(`Streaming Minutes Watched` = sum(`Streaming Minutes Watched`, na.rm = TRUE)) %>%
  arrange(Month)

ggplot(data = smw_yl, aes(x = Month, y = `Streaming Minutes Watched`, group = 1)) +
  geom_line(color = "steelblue", linewidth = 1) +
  geom_point(color = "steelblue", size = 2) +
  geom_smooth(method = "lm", se = FALSE, color = "darkgreen", linetype = "dashed") +
  scale_y_continuous(labels = comma) +
  labs(
    title = "Streaming Minutes Watched — Monthly Trend (Feb 2024 – Jan 2025)",
    caption = "Source: Digital Analytics Platform | Dashed line = linear trend"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

---

## Summary

All three KPIs show a consistent upward trend across the annual cycle, with Q4 and January performance outpacing the mid-year period. The linear trend lines confirm this directional growth is not noise — each metric is on a meaningful upward trajectory.

This analysis was produced using R (ggplot2, dplyr, tidyr) and was designed to be reproduced monthly by updating the source data frames. In a live workflow, these data frames would be replaced by imports from the platform's analytics API or exported CSV files.
